Open archaeology, open source?

### 2023-10-17 analysis/_03-data_methodology.qmd
Filter non-archaeology items

@@

>>>>

```{r data-oarch-filter}
oarch_filter <- read_csv(here("analysis/data/raw_data/open-archaeo_filter.csv"))
n_items_removed <- nrow(filter(oarch_filter, !item_name %in% oarch$item_name))
oarch |>
  filter(!item_name %in% oarch_filter$item_name) ->
  oarch

# Exclude from GitHub API data collection because does not have own repo
oarch$gh_repo[oarch$item_name == "ArchaeoLines"] <- NA
```

@@

We excluded `r n_items_removed` records from open-archaeo from this analysis because they did not fit our "made by archaeologists, for archaeologists" criteria.

### 2023-10-17 analysis/_06-network.qmd
Filter non-archaeology items

# Cleaning
oarch_graph |>
  rename(user = author) |>
  # Remove non-human users
  filter(!str_detect(user, coll("[bot]"))) |>
  filter(!user %in% c("ghost", "codecov-io", "coveralls", "codecov-commenter",
                      "gitter-badger", "dependabot-support")) |>
  # Remove big, non-archaeology projects that flood the network
  filter(!repo %in% c("Stellarium/stellarium", 
                     "opengisch/QField",
                     "lutraconsulting/input")) ->
  oarch_graph
```

>>>>

# Cleaning
oarch_graph |>
  rename(user = author) |>
  # Remove non-human users
  filter(!str_detect(user, coll("[bot]"))) |>
  filter(!user %in% c("ghost", "codecov-io", "coveralls", "codecov-commenter",
                      "gitter-badger", "dependabot-support")) ->
  oarch_graph
```
